Supplementary Figures: Quality control for the target decoy approach for peptide identification

### 2022-11-17 authors.tex
update paper_figures with tiff files

\author{Milan Malfait}
\affiliation[Ghent University]
{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}

\author{Ralf Gabriels}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Arthur Declerq}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Adriaan Sticker}
\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
\alsoaffiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Lennart Martens}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

>>>>

\author{Milan Malfait}
\affiliation[Ghent University]
{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
\alsoaffiliation[Janssen]{Statistics and Decision Sciences, Janssen Pharmaceutical Companies of Johnson and Johnson, Beerse, Belgium}

\author{Ralf Gabriels}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Ghent, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Arthur Declerq}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Ghent, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Adriaan Sticker}
\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
\alsoaffiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Ghent, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Lennart Martens}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Ghent, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

### 2022-11-17 supplementaryBackMatter.tex
update paper_figures with tiff files

% Options for packages loaded elsewhere
% Motified template from 
% https://github.com/jgm/pandoc/blob/master/data/templates/default.latex
% Removed author
% Removed natbib
% to comply with achemso document class
% authors in author.tex via includes: in_header:
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  journal=jprobs,
  manuscript=article]{achemso}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\author{Elke Debrie}
\affiliation[Ghent University]
{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}

\author{Milan Malfait}
\affiliation[Ghent University]
{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}

\author{Ralf Gabriels}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Arthur Declerq}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Adriaan Sticker}
\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
\alsoaffiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Lennart Martens}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Lieven Clement}
\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
\email{lieven.clement@ugent.be}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
%natbib deleted from template

\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary Figures: Quality control for the target decoy approach for peptide identification},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary Figures: Quality control for the target decoy approach for peptide identification}
% remove author
\date{}

\begin{document}
\maketitle

@@

  \bibliography{biblio.bib}

\end{document}

>>>>

\newpage

\section{Supplementary Figures}

\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\figurename}{Supplementary Figure}

@@
